Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-02 main.tex
Comments

\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
      \cite{DBLP:conf/eurosp/SchoepeBPS16} 
\item Nick and Andre's papers (and other micropolicy papers)
\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item {https://arxiv.org/pdf/1811.02787.pdf}
\item {https://arxiv.org/pdf/1902.05283.pdf}
\item {http://cs.au.dk/~lask/papers/esop2018.pdf}
\item {https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

@@

\item Mechanized Reasoning about a Capability Machine: [Linn] Georges,
Trieu, Birkedal (PriSC 2020).
%
Described at the Iris Workshop as formalizing the security properties of
capabilities. This appears to involve a fairly complex and very large
mechanization in Iris (also in the eyes of the Iris people).
\end{itemize}

@@

\begin{itemize}
\item Variations / extensions (OS, multiple processes, coroutines, generalizing depths to stacks of static call points, etc.)
\item Extending the policy / property to more realistic ones
\begin{itemize}
\item Argument passing
\item Variable-size stack frames
\item Stack variables
\item Relation to Nick and Andre’s policy
\end{itemize}
\item Could we also implement all this using Cheri capabilities?
\end{itemize}

>>>>

\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
      \cite{DBLP:conf/eurosp/SchoepeBPS16}
\item Nick and Andre's papers (and other micropolicy papers)
\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item \url{https://arxiv.org/pdf/1811.02787.pdf}
\item \url{https://arxiv.org/pdf/1902.05283.pdf}
\item \url{http://cs.au.dk/~lask/papers/esop2018.pdf}
\item \url{https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

@@

\item Mechanized Reasoning about a Capability Machine: [Linn] Georges,
Trieu, Birkedal (PriSC 2020).
%
Described at the Iris Workshop as formalizing the security properties of
capabilities. This appears to involve a fairly complex and very large
mechanization in Iris (also in the eyes of the Iris people).

\item \url{https://www.cis.upenn.edu/~stevez/papers/LZ05a.pdf}

\item We'd better say something about the relation to the original
hyperproperties paper, no?
\end{itemize}

@@

\begin{itemize}
\item Variations / extensions (OS, multiple processes, coroutines, generalizing depths to stacks of static call points, etc.)
\item Extending the policy / property to more realistic ones
\begin{itemize}
\item Argument passing
\item Variable-size stack frames
\item Stack variables
\item Relation to Nick and Andre’s policy
\end{itemize}
\item Could we also implement all this using Cheri capabilities?
\item A more abstract presentation, perhaps unifying our treatments of
confidentiality and integrity?
\end{itemize}
